---
output: github_document
---

[![Build Status](https://travis-ci.org/oganm/diceSyntax.svg?branch=master)](https://travis-ci.org/oganm/diceSyntax) [![codecov](https://codecov.io/gh/oganm/diceSyntax/branch/master/graph/badge.svg)](https://codecov.io/gh/oganm/diceSyntax)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::load_all()
set.seed(12345)
```


diceSyntax
=================

```{r}
roll('4d6') # roll 4d6

roll('4d6k3') # roll 4d6 keep 3 highest

roll('4d6kl3') # roll 4d6 keep lowest 3

roll('4d6d1') # roll 4d6 drop 1 lowest

roll('4d6dh1') # roll 4d6 drop highest 1

roll('4d6+3') # roll 4d6 add 3

roll('4d6r1r2') # roll 4d6 reroll 1s and 2s

roll('4d6r<2') # same as above

roll('4d6r1ro2') # roll 4d6 reroll 1s but reroll 2s only once

roll('5d2!') # exploding dice

roll('5d2!!') # compounding dice

r('1d6') # shortcut function

```


Other variables that `roll` funciton accepts are

- `critMark`: `TRUE` by default. If `TRUE` it adds stars around the dice roll in printed output if it is max or min value for the dice
- `vocal`: `TRUE` by default. If `FALSE` disables printing of dice rolls
- `returnRolls`: `FALSE` by default. If `TRUE` returns a list instead of an integer that includes rolled and dropped dice along with the dice sum

```{r}
r("10d10dl3",returnRolls = TRUE, vocal = FALSE)
```

Dice stats
----------------

Probabilities of outcomes can be calculated with `diceProb` function

```{r}
diceProb('4d6d1') %>% plot(names(.) %>% as.numeric(),.)

```


